\huge A Better (One-Line!) Title Here

### 2016-10-17 pets2017-paper/pets2017-paper.tex
shuffle sections and reword headings.
scrap the title.
another pass through the introduction.

  \title{\huge Tor's Usability for Censorship Circumvention}
  %Internet Freedom Made Easy: On Improving Tor’s Usability for Censorship Circumvention
  %Towards Usable Censorship Circumvention

  \runningtitle{Tor's Usability for Censorship Circumvention}

@@

Tor~\cite{dingledine2004tor} is an anonymity network that routes Internet traffic through a series of relays 
that make it difficult to observe the source and destination. 
Tor Browser~\cite{torbrowser}, a modified Firefox browser with a built-in Tor client, 
is the recommended way to use Tor. Tor Launcher is a Tor Browser component that
starts, stops, and otherwise controls the underlying Tor processes.
Tor Launcher's graphical user interface asks the user to configure
bridges, pluggable transports, and proxies to make a connection to Tor (we refer to as the ``configuration interface'' throughout this paper). This is the object of our study.

We start by introducing terms (section~\ref{sec:background}) and, 
describing the experimental setup (section~\ref{sec:environments}). 
Then we report of user observations and interviews (section~\ref{sec:qualitative}),
evaluate the current interface (section~\ref{sec:eval}), 
list design principles and interface changes (section~\ref{redesign}),
measure the impact of changes in the quantitative experiment in section~\ref{sec:quantitative}, 
testing measured the impact of the design changes (Section~\ref{sec:quantitative}, and
discuss user behaviors (section~\ref{sec:discussion}).
We end with limitations (section~\ref{sec:limitations}), 
related work (section~\ref{sec:related}), 
future work (section~\ref{sec:future}), and
a conclusion (section~\ref{sec:conclusion}).

We contribute:
\smallskip
\begin{itemize}
\item an evaluation of the current configuration interface
\item a redesigned configuration interface
\item logs of 114 users' connection attempts
\item failure modes seen during connection attempts
\item recommended interface changes
\item alternative bootstrapping approaches
\end{itemize}
We hope that our work helps users circumvent censorship and connect to Tor.

@@

\begin{figure}
  \centering
    \includegraphics[width=0.5\textwidth]{bridge-options.png}
%\small
%\begin{itemize}
%\renewcommand{\labelitemi}{$\circ$}
%\item Connect with provided bridges\\
%Transport type:
%\begin{itemize}
%\item flashproxy
%\item fte
%\item fte-ipv6
%\item meek-amazon
%\item meek-azure
%\item meek-google
%\item obfs3 (recommended)
%\item obfs4
%\item scramblesuit
%\end{itemize}
%\item Enter custom bridges\qquad\fbox{Help}\\
%\end{itemize}
\caption{
Bridge selection options in Tor Launcher for Tor Browser~5.0.3.
Users are not familiar with the options under ``Transport type,'' which are various
built-in circumvention technologies (``pluggable transports'').
Under ``Enter custom bridges,'' there is a space to paste in
a bridge line, obtained out of band.
The ``Help'' button displays instructions on obtaining
bridge lines. 
}
\label{fig:bridge-options}
\end{figure}

@@

\subsection{Potential for good} 
%Tor's anonymizing functionality also circumvents censorship. Using Tor for censorship circumvention became sufficiently common that many countries attempt to block Tor for this reason~\cite{winter2012great}. Today, Tor explicitly provides support for censorship circumvention through a network of unlisted relays as entry points into the Tor network, various methods of obfuscation to make connections to the Tor network less obvious, and advanced techniques to resist blocking.

@@

\section{Experimental Setup}
\label{sec:environments}
For our experiments, we use instrumented versions of Tor Browser~5.0.3, 
the most recent stable release at the time~\cite{torbrowser-503}.
Though there were new releases during the experiments,
we used the same version across all participants to not introduce
confounding factors.

@@

\subsection{Discussion} 
We talk about the failure cases and behavioral trends observed in our quantitative user study and recommend some changes to the Tor configuration interface based on those observations.

@@

\section{Limitations} 
The configuration interface uses the native operating system's elements and their respective styling, so an interface looks slightly different across different operating systems. We only tested interface on Windows machines, which were the machines available at <redacted>. %Xlab. 
Participants who are not accustomed to Windows machines may have been slower to complete the given task, but this affected all conditions equally.

@@

\section{Future Work} 
%In principle, the process of configuring a proxy and bridge can be automated, but
%the interface eschews automatic configuration through network probing
%in favor of guided manual configuration to give users agency in configuring their connection. 
%Automatic configuration through network probing may put some users in certain regimes at risk. 
%A knowledgeable user can minimize their network trace and hide that they are connecting to Tor.
%However, this requires that the user grapple with technical concepts such as 
%bridges, pluggable transports, and proxies. Some of these concepts are specific to 
%Tor and not general concepts.

@@

\section{Conclusion} 
We conducted a series of experiments to improve the Tor Browser 5.0.3 configuration interface, focusing on users who use Tor to circumvent censorship. Since connecting to the Tor network unsuccessfully indicates to network eavesdroppers that users are connecting to Tor, the configuration process is manual to allow users to have control over the network activity. Through interviews and lab studies, we find that users have difficulty configuring network components to circumvent censorship, because they do not know how censorship or Tor works. We detail the common challenges, our changes to the configuration interface address those challenges, and the recommendations we have for Tor in this paper.

%\section {Resources} 
%For additional details, such as the censorship simulation code, interview transcriptions, and logs of participant interactions, we refer you to the project repository: \\
%
%\noindent \url{https://github.com/lindanlee/circumvention-ux-tor}
%
%\section {Acknowledgments}
%I want to especially thank Rowilma del Castillo of Xlab for supporting the experiment, assisting with testing, and being flexible with non-Xlab recruiting. I have received much valuable feedback from Nima Fatemi, Isabela Bagueros, Georg Koppen, and the Tor UX team.

\appendix

>>>>

  \title{\huge A Better (One-Line!) Title Here}

  \runningtitle{Ugh!}

@@

Tor~\cite{dingledine2004tor} is an anonymity network that routes Internet traffic through a series of relays 
that make it difficult to observe the source and destination. 
Tor Browser~\cite{torbrowser} is a modified Firefox browser with a built-in Tor client that
is the recommended way to use Tor. Tor Launcher is a Tor Browser component that
starts, stops, and otherwise controls the underlying Tor processes.
Tor Launcher's graphical user interface asks the user to configure
bridges, pluggable transports, and proxies to make a connection to Tor (we refer to this graphical user interface as the ``configuration interface'' throughout this paper). This is the object of our study.

We hope that our work helps users more easily connect to Tor. The direct and obvious benefit of our work is that is that it may help users who would have previously been unable to configure Tor Browser to use it or that it may save time for users who would have been able to configure a valid connection to the Tor. Improving the user experience through user testing has the potential to be beneficial for both the software company (less help desk tickets) and the end users (less frustration).

However, we believe that our work uniquely necesssary and beneficial to Tor Browser. Although originally designed for Internet anonymity, using Tor Browser to circumvent censorship has now become sufficiently common that many countries now attempt to block Tor relays for this reason~\cite{winter2012great}. Our experiment to design an easier bootstrapping process will especially benefit citizens who face Internet censorship. If successful, an increase in overall users means more than user growth, but an increased anonymity set~\cite{dingledine2006anonymity}. \\

\noindent This paper contributes:
\smallskip
\begin{itemize}
\item an evaluation of the current configuration interface
\item a redesigned configuration interface
\item logs of 114 users' connection attempts
\item failure modes seen during connection attempts
\item recommended interface changes
\item alternative bootstrapping approaches
\end{itemize}

We start by introducing relevant concepts (section~\ref{sec:background}) and
defining the scope of our experiment (section~\ref{sec:scope}). 
Then, we report user observations and interviews (section~\ref{sec:qualitative}),
list design principles and interface changes (section~\ref{redesign}),
state evaluation criteria for testing the interface (section~\ref{sec:eval}), 
and measure the impact of our design changes (Section~\ref{sec:quantitative}).
We end with a discussion on what we learned (section~\ref{sec:discussion}),
limitations of out experiment (section~\ref{sec:limitations}), 
a look at our work in the context of existing work (section~\ref{sec:related}), and
a brief conclusion (section~\ref{sec:conclusion}).

%%%%%% LINDA'S PASS UP TO HERE %%%%%%%%%

@@

\begin{figure}
  \centering
    \includegraphics[width=0.5\textwidth]{bridge-options.png}
\caption{
Bridge selection options in Tor Launcher for Tor Browser~5.0.3.
Users are not familiar with the options under ``Transport type,'' which are various
built-in circumvention technologies (``pluggable transports'').
Under ``Enter custom bridges,'' there is a space to paste in
a bridge line, obtained out of band.
The ``Help'' button displays instructions on obtaining
bridge lines. 
}
\label{fig:bridge-options}
\end{figure}

@@

\subsection{Motivation} 
%Tor's anonymizing functionality also circumvents censorship. Using Tor for censorship circumvention became sufficiently common that many countries attempt to block Tor for this reason~\cite{winter2012great}. Today, Tor explicitly provides support for censorship circumvention through a network of unlisted relays as entry points into the Tor network, various methods of obfuscation to make connections to the Tor network less obvious, and advanced techniques to resist blocking.

@@

\section{Scope}
\label{sec:scope}
%insert explanation into why we did what we did here.

For our experiments, we use instrumented versions of Tor Browser~5.0.3, 
the most recent stable release at the time~\cite{torbrowser-503}.
Though there were new releases during the experiments,
we used the same version across all participants to not introduce
confounding factors.

@@

\section{Discussion} 
\label{sec:discussion}
We talk about the failure cases and behavioral trends observed in our quantitative user study and recommend some changes to the Tor configuration interface based on those observations.

@@

\section{Limitations}
\label{sec:limitations}
The configuration interface uses the native operating system's elements and their respective styling, so an interface looks slightly different across different operating systems. We only tested interface on Windows machines, which were the machines available at <redacted>. %Xlab. 
Participants who are not accustomed to Windows machines may have been slower to complete the given task, but this affected all conditions equally.

@@

\section{Conclusion} 
\label{sec:conclusion}
We conducted a series of experiments to improve the Tor Browser 5.0.3 configuration interface, focusing on users who use Tor to circumvent censorship. Since connecting to the Tor network unsuccessfully indicates to network eavesdroppers that users are connecting to Tor, the configuration process is manual to allow users to have control over the network activity. Through interviews and lab studies, we find that users have difficulty configuring network components to circumvent censorship, because they do not know how censorship or Tor works. We detail the common challenges, our changes to the configuration interface address those challenges, and the recommendations we have for Tor in this paper.

%\section {Resources} 
%For additional details, such as the censorship simulation code, interview transcriptions, and logs of participant interactions, we refer you to the project repository: \\
%
%\noindent \url{https://github.com/lindanlee/circumvention-ux-tor}
%
%\section {Acknowledgments}
% Rowilma del Castillo of Xlab supported out experiment by assisting with testing, offering recruitment services, and allowing experiments after-hours. Nima Fatemi, Isabela Bagueros, Georg Koppen, and the Tor UX team have provided me with valuable feedback along the way.

\appendix
\section{Alternative Approaches} 
%In principle, the process of configuring a proxy and bridge can be automated, but
%the interface eschews automatic configuration through network probing
%in favor of guided manual configuration to give users agency in configuring their connection. 
%Automatic configuration through network probing may put some users in certain regimes at risk. 
%A knowledgeable user can minimize their network trace and hide that they are connecting to Tor.
%However, this requires that the user grapple with technical concepts such as 
%bridges, pluggable transports, and proxies. Some of these concepts are specific to 
%Tor and not general concepts.

@@
